\section{Adding a new instruction group for error injections}
\label{sec:new_inst_group}

As mentioned in Section~\ref{sec:where}, SASSIFI can be extended to include
custom instruction groups. Here we outline the changes needed to add a new
instruction group to SASSIFI. 

\begin{itemize}
\item Assign a name to the new instruction group (e.g., NEW\_OP) and add it to
the {\it enum INST\_TYPE} in err\_injector/error\_injector.h. Include it in the
instCatName array in the same file. 

\item Identify the SASSI opcodes that should be included in this new group and
update the get\_op\_category function in err\_injector/error\_injector.h
accordingly. The list of available opcodes can be found in the sassi-opcodes.h.

\item Specify what to do in the sassi\_after\_handler for error injection. For
the IOV mode injections, simply add a {\it case} in the
{\it switch} statement in the sassi\_after\_handler function in
err\_injector/injector.cu, similar to the IADD\_IMUL\_OP.  For the IOA mode injections, add an
{\it if} statement in the sassi\_after\_handler function similar to the STORE\_OP instructions.

\item Update the scripts such that error injection sites will be created and
injection jobs will be launched for the new instruction group. Update the
categories of the instruction types in scripts/common\_params.py such that it
matches the  {\it enum INST\_TYPE} in err\_injector/error\_injector.h.  Finally
add the new instruction group and the associated bit-flip models in the
inst\_value\_igid\_bfm\_map or inst\_address\_igid\_bfm\_map in scripts/specific\_params.py.

\end{itemize}


\section{Bug reports}

We plan to track issues using GitHub's issue tracking features.

\section{Abbreviations}

This document and the SASSIFI source code uses many abbreviations and we list important ones here:

{\bf SASSIFI}: SASSI-based Fault Injector 

{\bf RF}: Register File

{\bf AVF}: Architecture Vulnerability Factor 

{\bf RF mode}: Injection mode in which the register selected for injection is
independent of the instruction executing at the time of injection. This mode is
used to analyze RF AVF. 

{\bf IOV mode}: Injection mode in which the value selected for injection is
dependent on the instruction executing at the time of injection. We inject errors 
in the output value of the instruction that just executed. This mode
allows us to perform targeted error injections on various instruction groups.

{\bf IOA mode}: Injection mode in which the address selected for injection is
dependent on the instruction executing at the time of injection. We inject
errors either in the register index or store address of the instruction that
just executed, based on the instruction type. This mode allows us to perform
targeted error injections to study the sensitivity of address errors. 

{\bf SDC}: Silent Data Corruption 

{\bf DUE}: Detected Uncorrectable Error 

{\bf Pot DUE}: Potential DUE (could be detected if proper checkers are in place) 

{\bf BFM}: Bit-Flip Model 

{\bf IGID}: Instruction Group ID 

{\bf GPR}: General Purpose Register

{\bf CC}: Condition Code register

{\bf PR}: Predicate Register 

